Designing and Developing a Personalised Recommender System

### 2021-02-03 paper/paper.tex
filtered business json to csv restaurants only
filtered dataset to restaurants only

\subsection{Data preparation and feature selection}
Prepare data
Of the 209,393 businesses in the dataset, 168,903 are still open.
The entire Yelp dataset is huge and much of it is not necessary for my domain of bars.
As such I prepared the data by eliminating any data not relevant to my domain.
I selected features such as user ratings and a particular user's average rating,
since if a user typically rates places they go highly, but rates a particular bar low,
this is more significant than a user who always rates places low.

>>>>

\subsection{Data preparation and feature selection}
Prepare data
Of the 209,393 businesses in the dataset, 168,903 are still open. 
There are 43,980 restaurants which are open and contain 'Restaurant' as one of the categories. 
502 businesses in the overall dataset don't list anything in their categories section. 
43,052 businesses had at least 1 check-in. 
There are 4,223,201 reviews of restaurants. 
695,951 tips for these restaurants. 
1,968,703 users. 
43,992 restaurants listed with covid features, 8 restaurants which make up 12 duplicate entries 
(8 have 2 entries and 4 have 3 entries), the only difference between their entries being in the 
"Virtual Services Offered" section. 
The entire Yelp dataset is huge and much of it is not necessary for my domain of bars.
As such I prepared the data by eliminating any data not relevant to my domain.
I selected features such as user ratings and a particular user's average rating,
since if a user typically rates places they go highly, but rates a particular bar low,
this is more significant than a user who always rates places low.
